A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-04-14 01-intro.tex
Fix prepositions in Introduction

\begin{description}
\item[Memory Boundedness:]
At compile time, we can ensure that the program fits in the device's restricted
memory and that it will not grow unexpectedly during runtime.
\item[Deterministic Execution:]
We can simulate an entire program execution providing an input history with the
guarantee that it will always have the same behavior.
This can be done in negligible time in a controlled development environment by
multiple developers before deploying the application in the actual device.
\item[Terminating Reactions:]
Real-time applications must guarantee responses within specified deadlines.
A terminating semantics enforces upper bounds for all reactions and guarantees
that programs always progress with the time.
In addition, it also ensures that programs always reach an idle state amenable
to entering in standby mode, which can improve the autonomy of battery-powered
devices.
\end{description}

>>>>

\begin{description}
\item[Memory Boundedness:]
At compile time, we can ensure that the program fits in the device's restricted
memory and that it will not grow unexpectedly during runtime.
\item[Deterministic Execution:]
We can simulate an entire program execution providing an input history with the
guarantee that it will always have the same behavior.
This can be done in negligible time in a controlled development environment by
multiple developers before deploying the application to the actual device.
\item[Terminating Reactions:]
Real-time applications must guarantee responses within specified deadlines.
A terminating semantics enforces upper bounds for all reactions and guarantees
that programs always progress with time.
In addition, it ensures that programs always reach an idle state amenable
to entering in standby mode, which can improve the autonomy of battery-powered
devices.
\end{description}
